Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-23 paper.qmd
Changed number of bins in MNIST

<!-- Fit the model and compute error-->
```{r}
#| label: hexbin-mnist
## Compute hexbin parameters
num_bins_x_mnist <- 22
lim1 <- mnist_scaled_obj$lim1
lim2 <- mnist_scaled_obj$lim2
r2_mnist <- diff(lim2)/diff(lim1)

>>>>

<!-- Fit the model and compute error-->
```{r}
#| label: hexbin-mnist
## Compute hexbin parameters
num_bins_x_mnist <- 19
lim1 <- mnist_scaled_obj$lim1
lim2 <- mnist_scaled_obj$lim2
r2_mnist <- diff(lim2)/diff(lim1)
